Parallel Multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-09-04 hpmoon-hpca.tex
Corrections here and there

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. We have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) that
could lead to different execution times, so it would be difficult to
compare different times and quality solutions at the same time.

@@

The ECJ framework \citep{ECJ} has been used to run the
experiments. Specific operators have been developed as new modules for
ECJ, and they can be downloaded from our GitHub repository under a
LGPL V3 License
%\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
The
island model has been executed synchronously, using the ECJ Internal
Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520
@2.27GHz, 16 GB RAM, with Java Version 1.6.0\_16.

@@

@@

High-performance problems that require a large number of decision variables can leverage the division of the decision space that parallel and distributed algorithms imply. This can be done in dMOEAs by dividing the chromosome into different parts, each one modified by a different island. This paper compares a baseline distributed NSGA-II with three different strategies to separate the chromosome (disjoint or overlapping parts), using a high number of islands. Results show that these methods can achieve better quality metrics than the baseline in the same amount of time, with larger chromosome lengths.

Results also show that when increasing the number of islands, the adaptive overlapping method significantly improves the results with respect to the disjoint and overlapped methods. However, this is only apparent with larger chromosome sizes. Therefore, the length of the chromosome is also a key factor to take into account in adaptive methods, and not only the number of islands. Studying this factor with more types of problems, and new configurations of population size and chromosome lengths will be addressed in the future.%
%

Also, more distributed implementations in several systems (such as a GPUs or heterogeneous clusters) with more different quantities of islands/processors, will be used to perform a scalability study of the different methods, being the transmission time between islands a relevant issue to address. Finally, new benchmarks and real problems will also be  used to validate this approach.

>>>>

The criterion used for terminating an experiment has been the running
time: 25 seconds for dimension 512 and 100s (four times more) for
2048. We have used time instead of the number of evaluations firstly
because our hypothesis argues that the time saved in crossover and
mutation can be spent on improving the sub-populations and more
operations and migrations can be achieved. Also, we are using
different number of islands (with different sub-population sizes) and that
could lead to different execution times, so it would be difficult to
compare different times and quality of solutions at the same time.

@@

The ECJ framework \citep{ECJ} has been used to run the
experiments. Specific operators have been developed as new modules for
ECJ, and they can be downloaded from our GitHub repository under a
LGPL V3 License
%\footnote{\url{https://github.com/hpmoon/hpmoon-islands}}. 
\footnote{\url{https://ANONYMOUS-REPOSITORY}}. 
The
island model has been executed synchronously, using the ECJ Internal
Island Model, in a CentOS 5.4 machine with Intel(R) Xeon(R) CPU E5520
@2.27GHz, 16 GB RAM and Java Version 1.6.0\_16.

@@

\#Islands	&	B		&	D		&	O			&	A			&	B		&	D			&	O			&	A			&	B		&	D		&	O		&	A					\\ \hline

@@

High-performance problems % problems are not high-performance. They
                          % _require_ high performance
 that require a large number of decision variables can leverage the
 division of the decision space that parallel and distributed
 algorithms imply. This can be done in dMOEAs by dividing the
 chromosome into different parts, each one modified by a different
 island. This paper compares a baseline distributed NSGA-II with three
 different strategies to separate the chromosome (disjoint or
 overlapping parts), using a high number of islands. Results show that
 these methods can achieve better quality metrics than the baseline in
 the same amount of time, with larger chromosome lengths.

Results also show that when increasing the number of islands, the
adaptive overlapping method significantly improves the results with
respect to the disjoint and overlapped methods. However, this is only
apparent with larger chromosome sizes. Therefore, the length of the
chromosome is also a key factor to take into account in adaptive
methods, and not only the number of islands. Studying this factor with
more types of problems, and new configurations of population size and
chromosome lengths will be addressed in the future.% 
% More discussion should be added. Why is adaptive better? Is the high
% performance really needed? - JJ

Also, more distributed implementations in several systems (such as a
GPUs or heterogeneous clusters) with different amounts of
islands/processors, will be used to perform a scalability study of the
different methods, being the transmission time between islands a
relevant issue to address. Finally, new benchmarks and real problems
will also be  used to validate this approach.
